Understanding the Landscape of Childlessness in the U.S.

### 2024-03-18 outputs/paper/paper.qmd
finalize paper

# Plot the data
ggplot(data_long_class, aes(x = Year, y = Percentage, color = `Class Identification`)) +
   geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Class", color = "Breakdown Category") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

Further, @tbl-nochild-degree explores the association between educational attainment and childlessness. @fig-nochild-class-edu illustrates this data, presenting a comparative analysis of childlessness across individuals with different levels of educational attainment (less than high school, high school and college degree or higher) in the United States from 1972 to 2022. The graph utilizes line trends to depict the percentage of childless individuals within each degree category over the five decades.

@@

>>>>

# Plot the data
ggplot(data_long_class, aes(x = Year, y = Percentage, color = `Class Identification`)) +
   geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Class", color = "Class") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

Further, @tbl-nochild-degree explores the association between educational attainment and childlessness. @fig-nochild-class-edu illustrates this data, presenting a comparative analysis of childlessness across individuals with different levels of educational attainment (less than high school, high school and college degree or higher) in the United States from 1972 to 2022. The graph utilizes trend lines to depict the percentage of childless individuals within each degree category over the five decades.

@@

Upon assessing the available data, we further extrapolate on them here by calculating the average rate of childlessness in each year for each of these four critical factors: health conditions, marital status, educational attainment and socio-economic class. At the end, @fig-overall compounds on these factors as a graph that shows the overall rate of childlessness in each year from 1972 to 2022.
